An in-depth study of Explainability and Adversarial Robustness for RNNs

### 2019-12-12 ex3/paper/paper.tex
Modified adv section

\subsection{Evaluation}
\begin{figure}
\includegraphics[width=\columnwidth]{../plots/adv_comparison/tradeoff.pdf}
% \includegraphics[width=0.49\textwidth]{adv_plots/cwl1.pdf}
% \includegraphics[width=0.49\textwidth]{adv_plots/cwl2.pdf}
\caption{Performance of \gls{cw} with different $\epsilon$ values.}
\todo{I guess the irregularity at eps=1 hints at too few iterations. Currently rerunning with 1000 base iterations}
\label{fig:adv_cw}
\end{figure}
\autoref{fig:adv_cw} depicts the ratio of attack flows which were successfully misclassified as benign with respect to the final packet along with the resulting distance from the original sample. Evidently, the larger the tradeoff $\epsilon$, the better the attack works, but also average distances from original flows become larger.
Hence, with acceptable distance values we were able to generate adversarial samples for about 80\% of attack samples.

The figure suggests that a tradeoff value between 0.5 and 1 would be ideal to find adversarial samples with a low enough distance from real samples. This conclusion might be misleading, however, as the distance cannot become larger anymore as soon as an adversarial sample has been found, when performing optimization as depicted by the objective function \eqref{eq:carliniWagner}. Hence, the depicted increase of average distances presumably is due to samples for which no adversarial sample was found for lower $\epsilon$ values.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{../plots/adv_comparison/adv_comparison_17.pdf}
\caption{Attack success ratios for both dataset and per attack family for CIC-IDS-2017. Depicted are flow detection accuracies for adversarial flows and for unmodified flows.}
\label{fig:adv_per_family}
\end{figure}

@@

\autoref{tab:adv_accuracies} depicts the performance for FGSM and $\ell_\infty$-bounded \gls{pgd}. 
As expected, while FGSM is the fastest of all algorithms, it delivers the worst performance. Of the investigated algorithms,  \gls{cw}  delivered the best performance.
\autoref{fig:adv_per_family} depicts how successful the attack is for individual attack families.  The table shows significant differences for detecting different attack families in the first place. However, also for generating adversarial flows some attack families are more susceptible than others.

For \autoref{tab:adv_accuracies} and \autoref{fig:adv_per_family} we used \gls{cw} with a tradeoff of 1. To provide a fair comparison, for \gls{fgsm} and \gls{pgd} we used an $\ell_\infty$ distance which we observed for \gls{cw}.

It is interesting to note that also increasing the $\ell_\infty$ bound for \gls{pgd} did not result in significantly improved performance. We can thus confirm the recommendation by \cite{carlini_towards_2017} to perform gradient descent on the logit output instead of the loss.

>>>>

\begin{figure}[t]
\includegraphics[width=\columnwidth]{../plots/adv_comparison/adv_comparison_17.pdf}
\caption{Attack success ratios for both dataset and per attack family for CIC-IDS-2017. Depicted are flow detection accuracies for adversarial flows and for unmodified flows.}
\label{fig:adv_per_family}
\end{figure}

\subsection{Evaluation}
\autoref{fig:adv_per_family} depicts the performance for the investigated algorithms for both datasets and for each attack family in CIC-IDS-2017. 
We used \gls{cw} with a tradeoff of 1 and, to provide a fair comparison, for \gls{fgsm} and \gls{pgd} we used an average $\ell_\infty$ distance as observed for \gls{cw}.

As expected, \gls{cw}  delivers the best performance and FGSM, while being the fastest of all investigated algorithms, delivers the worst performance.
%\autoref{fig:adv_per_family} depicts how successful the attack is for individual attack families.
The figure shows significant differences for detecting different attack families in the first place. However, also for generating adversarial flows some attack families are more susceptible than others. However, the results match to a high degree with our expectations. For example, SQL injection attacks apparently are closer to normal traffic than \gls{dos} attacks and, hence, finding adversarial samples should be easier.

It is interesting to note that increasing the $\ell_\infty$ bound for \gls{pgd} did not yield significantly improved performance. We can thus confirm the recommendation by \cite{carlini_towards_2017} to perform gradient descent on the logit output instead of the loss for good results.

\autoref{fig:adv_cw} depicts the success ratio and average distance for \gls{cw} for different tradeoffs $\epsilon$.
%\autoref{fig:adv_cw} depicts the ratio of attack flows which were successfully misclassified as benign with respect to the final packet along with the resulting distance from the original sample.
Evidently, the larger the tradeoff $\epsilon$, the better the attack works, but also distances from original flows become higher.
Hence, with acceptable distance values we were able to generate adversarial samples for about 80\% of attack samples.
The figure suggests that a tradeoff value between 0.5 and 1 would be ideal to find adversarial samples with a low enough distance from real samples.
This conclusion might be misleading, however, as due to the objective function \eqref{eq:carliniWagner} the distance cannot become larger anymore for one sample as soon as an adversarial sample has been found. %, when performing optimization as depicted by the objective function .
Hence, the depicted distance increase presumably is due to samples for which no adversarial sample could be found for lower $\epsilon$ values.

\begin{figure}[b]
\includegraphics[width=\columnwidth]{../plots/adv_comparison/tradeoff.pdf}
% \includegraphics[width=0.49\textwidth]{adv_plots/cwl1.pdf}
% \includegraphics[width=0.49\textwidth]{adv_plots/cwl2.pdf}
\caption{Performance of \gls{cw} with different $\epsilon$ values.}
\todo{I guess the irregularity at eps=1 hints at too few iterations. Currently rerunning with 1000 base iterations}
\label{fig:adv_cw}
\end{figure}

@@

@@
